\chapter{Introduction}

%In todays world with ongoing worldwide economic crisises like the COVID-19-pandemic or the Russia-Ukraine-Conflict, 
%the importance of trade policies are shown. Therefore the economy and worldwide scientists try to develop new models 
%and methods to predict the outcome of trade policies and their impact on the social welfare, the economic growth and the 
%equal distribution of those gains. One common view of trade policies is that the liberalization of trade promotes the
%economic growth, the developement and the reduction of poverty for countries. However, many countries, especially third world 
%countries with low social welfare tend to favor the protection of the domestic industries instead of opening the countries 
%economy for a worldwide free trade. Using new models and adapting those further regarding the possible benefits and costs for the 
%countries and their social welfare is a possible method to gain new information about the real impacts of trade liberalization
%and its' potential benefits. This aspect was analyzed and researched by Artuc et al. in 2019. Choosing several trade models
%and adapting those to make use of a huge dataset regarding third world countries to measure the impact of trade liberalization
In today's world with ongoing worldwide economic crises like the COVID-19-pandemic or the current Russia-Ukraine-conflict,
trade policies are seen and used as possible, important instruments to either help or punish specific countries' economies. 
However, the majority of countries currently suffers a decline in social welfare caused by those ongoing crises. Through new 
developed and improved trade models and the current worldwide economic situation, the interest in the impact of trade policies,
especially the trade liberalization, and the distribution of the gains from trade increased. While trade liberalization is 
commonly seen as economy and welfare enhancing, the majority of developing countries with low social welfare
still tend to restrict their trade in favor of protectionism. To estimate the impact of trade liberalization and the trade-off
between the income gains and inequality costs, Artuc, Rijkers and Porto reviewed recent and past trade models to measure 
income gains and inequality costs for 54 developing countries in their article from 2019. Using household survey data from 54
developing countries in combination with trade data and tariff data, they developed a new model to determine the income gains,
inequality costs and therefore the inequality adjusted income gains of trade. With the model, they were able to answer the
question, whether there are trade-offs between income gains and inequality costs in case of trade liberalization and whether
the trade liberalization is beneficial for the studied countries' welfare.\\

This paper reviews the study by Artuc, Rijkers and Porto and takes several critical aspects of the paper itself into consideration.
The first section describes the data used in the study and describes the three parts, the household survey data, the tariff data
and the trade data. The second section summarizes the methods of the study by Artuc et. al. and explains their results.
After that, the next section will showcase several critical aspects in regard of the data used in the study, 
the methods used to form their model and the results, to underline possible weaknesses and strengths of this study. 
Finally, a conclusion is given about the quality of the model and possible improvements for further use cases. 